Model Checking Differentially Private Properties

### 2018-01-30 specifications.tex
add bluetooth DoS description

We consider the Bluetooth example from the PRISM benchmarks \cite{prism-bluetooth-page}. The model is a
Markov chain, and it ...

For instance,
$\dpriv{\epsilon}{\delta} (\G   \F \mathit{discovered})$
specifies states having $(\epsilon, \delta)$-close
infinitely often $\mathit{discovered}$ behaviors to its neighbors.

>>>>

Consider the Bluetooth example in~\cite{prism-bluetooth-page} and the
formula $\dpriv{\epsilon}{\delta}{\F \G \mathit{timeout}}$. Let us say
two states are neighbors if the number of slave devices differs by at
most one. Then the formula holds if the probability of having
continuous time out (say, in the denial of service attack) is
$(\epsilon, \delta)$-close for all neighbors. That is, adding a slave
device cannot increase the chance of service failure significantly.
